---
title: "Number of In-Person versus Online Interactions in Daily Life During COVID-19 ~ Close Out-Degree"
author: "Ovidia Stanoi"
date: "2025-02-26"
output: html_document
---

### Prepare data for regression analyses. 
<br>

Remove all data from the global environment.<br>

```{r, message = F, warning = F}
remove(list=ls()) 
```
<br>

Load libraries.<br>

```{r, message = F, warning = F}
library("tidyverse")
library("rstanarm")
library("sjPlot")
library("brms")
library("ggpubr")
```
<br>

Specify your directory path below.<br>

```{r, message = F, warning = F}
path <- ""
```
<br>

Open dataset.<br>

```{r, message = F, warning = F}
covid_ema <- read.csv(sprintf("%s/Data/all_data_merged_clean.csv", path)) 
```
<br>

Extract for each participant their mean number of in-person and online interactions during the EMA period, as well as their number of close friend prior to the COVID-19 pandemic, their baseline demographic information, COVID-19 living conditions, number of stressors, and EMA completion rates. All these variables will be added in the regression model.<br>

```{r, message = F, warning = F}
df <- covid_ema %>%
  group_by(pID) %>%
  dplyr::summarise(groupID = unique(groupID), 
                   mean_PhysInt_NUM = mean(PhysInt_NUM, na.rm = T),
                   mean_SocInt_NUM = mean(SocInt_NUM, na.rm = T),
                   baseline_closest_deg_out_norm = unique(baseline_closest_deg_out_norm),
                   baseline_income_num = unique(baseline_income_num),
                   baseline_educ_parents_years = unique(baseline_educ_parents_years),
                   baseline_college_year = unique(baseline_college_year),
                   baseline_gender_numeric = unique(baseline_gender_numeric),
                   covid_housing_tension = unique(covid_housing_tension),
                   covid_phys_dist = unique(covid_phys_dist_avg), 
                   EMA_completion_rate = unique(EMA_completion_rate))
```
<br>

Center continuous predictors around the sample mean and binary variables around zero.<br>

```{r, message = F, warning = F}
df$baseline_closest_deg_out_norm_c <- df$baseline_closest_deg_out_norm - mean(df$baseline_closest_deg_out_norm, na.rm = T)
df$baseline_income_num_c <- df$baseline_income_num - mean(df$baseline_income_num, na.rm = T)
df$baseline_educ_parents_years_c <- df$baseline_educ_parents_years - mean(df$baseline_educ_parents_years, na.rm = T)
df$baseline_college_year_c <- df$baseline_college_year - mean(df$baseline_college_year, na.rm = T)
df$baseline_gender_numeric_c <- df$baseline_gender_numeric - .5
df$covid_housing_tension_c <- df$covid_housing_tension - mean(df$covid_housing_tension, na.rm = T)
df$covid_phys_dist_c  <- df$covid_phys_dist - mean(df$covid_phys_dist, na.rm = T)
df$EMA_completion_rate_c  <- df$EMA_completion_rate - mean(df$EMA_completion_rate, na.rm = T)
```
<br>

### Run regression models
<br>

##### Model 1: Outcome Variable = Mean Number of In-Person Interactions
<br>

**RQ**: Do people with more close friends in college have more interactions in-person on a typical day during the COVID-19 pandemic?<br>

Run regression analysis 1: mean number of in-person interactions ~ close out-degree.<br>

```{r}
options(mc.cores = parallel::detectCores())
fa <- stan_glmer(mean_PhysInt_NUM ~ baseline_closest_deg_out_norm_c +
                   baseline_income_num_c + baseline_educ_parents_years_c + baseline_college_year_c +
                   baseline_gender_numeric_c + covid_housing_tension_c + covid_phys_dist_c + 
                   EMA_completion_rate_c + (1 | groupID),
                 data = df, seed = 123)
save(fa, file = sprintf("%s/Models/2.a.Nr-InPerson_Interactions_Out-Degree.RData", path))
```
<br>

##### Model 2: Outcome Variable = Mean Number of Online Interactions
<br>

**RQ**: Do people with more close friends in college have more online interactions on a typical day during the COVID-19 pandemic?<br>

Run regression analysis 1: mean number of online interactions ~ close out-degree.<br>

```{r}
options(mc.cores = parallel::detectCores())
fb <- stan_glmer(mean_SocInt_NUM ~ baseline_closest_deg_out_norm_c +
                   baseline_income_num_c + baseline_educ_parents_years_c + baseline_college_year_c +
                   baseline_gender_numeric_c + covid_housing_tension_c + covid_phys_dist_c + 
                   EMA_completion_rate_c + (1 | groupID),
                 data = df, seed = 123)
save(fb, file = sprintf("%s/Models/2.a.Nr-Online_Interactions_Out-Degree.RData", path))
```
<br>

### Summarize results
<br>

Create a table that presents the parameter estimates from the two models together.<br>

```{r, message = F, warning = F}
tab_model(fa, fb, show.se = TRUE,
          show.r2 = TRUE, 
          dv.labels = c("Mean Number of In-Person Interactions",
                        "Mean Number of Online Interactions"),
          pred.labels = c("(Intercept)", 
                          "Close Out-Degree Prior to COVID19",
                          "HH Income",
                          "Parents' Education",
                          "Year in College",
                          "Female",
                          "HH Tension",
                          "Physical Distance",
                          "EMA Completion Rate"),
          file = sprintf("%s/Tables/2.a. Nr-InPerson-Online_Interactions_Out-Degree.html", path))
```
<br>

Below, extract the proportion of the posterior distribution that is above or below zero for each predictor of interest separately for the two regression model (mean number of in-person and online interactions).<br>
<br>

##### Model 1: Outcome Variable = Mean Number of In-Person Interactions
<br>

Extract the posterior distributions of the parameter estimates from the first regression model.<br>

```{r, message = F, warning = F}
posterior <- as.data.frame(as.matrix(fa))
```
<br>

Extract the number of individual points included in a posterior distribution.<br>

```{r, message = F, warning = F}
n <- length(posterior$baseline_closest_deg_out_norm_c)
n
```
<br>

Calculate the proportion of the posterior distribution that is higher than 0 for the main effect of close out-degree on the mean number of in-person interactions.<br>

```{r, message = F, warning = F}
round(length(which(posterior$baseline_closest_deg_out_norm_c > 0))/n*100,1)
```
<br>

Calculate the total $R^2$ for the model.<br>

```{r, message = F, warning = F}
round(mean(bayes_R2(fa)),2)
```
<br>

##### Model 2: Outcome Variable = Mean Number of Online Interactions
<br>

Extract the posterior distributions of the parameter estimates from the first regression model.<br>

```{r, message = F, warning = F}
posterior <- as.data.frame(as.matrix(fb))
```
<br>

Extract the number of individual points included in a posterior distribution.<br>

```{r, message = F, warning = F}
n <- length(posterior$baseline_closest_deg_out_norm_c)
n
```
<br>

Calculate the proportion of the posterior distribution that is higher than 0 for the main effect of close out-degree on the mean number of online interactions.<br>

```{r, message = F, warning = F}
round(length(which(posterior$baseline_closest_deg_out_norm_c > 0))/n*100,1)
```
<br>

Calculate the total $R^2$ for the model.<br>

```{r, message = F, warning = F}
round(mean(bayes_R2(fb)),2)
```
<br>