---
title: "Evening Affect ~ Close Out-Degree * Interaction Medium (Online)"
author: "Ovidia Stanoi"
date: "2025-02-26"
output: html_document
---

### Prepare data for regression analyses. 
<br>

Remove all data from the global environment.<br>

```{r, message = F, warning = F}
remove(list=ls()) 
```
<br>

Load libraries.<br>

```{r, message = F, warning = F}
library("tidyverse")
library("rstanarm")
library("sjPlot")
library("brms")
library("bmlm")
```
<br>

Specify your directory path below.<br>

```{r, message = F, warning = F}
path <- ""
```
<br>

Open dataset.<br>

```{r, message = F, warning = F}
covid_ema <- read.csv(sprintf("%s/Data/all_data_merged_clean.csv", path)) 
```
<br>

Create a new variable indicating the proportion of interactions reported on a given day that were online.<br>
```{r, message = F, warning = F}
covid_ema$prop_interact_online <- ifelse(!(is.na(covid_ema$NegativeMood)),
                                           covid_ema$SocInt_NUM/(covid_ema$SocInt_NUM + covid_ema$PhysInt_NUM),
                                         NA)
```
<br>  

Center the continuous predictors that represent between-individual differences around the sample mean; center binary variables around zero.<br>

```{r, message = F, warning = F}
# Extract for each participant their close out-degree, demographic information, and COVID-19 information
df <- covid_ema %>%
  group_by(pID) %>%
  dplyr::summarise(baseline_closest_deg_out_norm = unique(baseline_closest_deg_out_norm),
                   baseline_income_num = unique(baseline_income_num),
                   baseline_educ_parents_years = unique(baseline_educ_parents_years),
                   baseline_college_year = unique(baseline_college_year),
                   baseline_gender_numeric = unique(baseline_gender_numeric),
                   covid_housing_tension = unique(covid_housing_tension),
                   covid_phys_dist = unique(covid_phys_dist_avg))

# Center variables around the mean
df$baseline_closest_deg_out_norm_c <- df$baseline_closest_deg_out_norm - mean(df$baseline_closest_deg_out_norm, na.rm = T)
df$baseline_income_num_c <- df$baseline_income_num - mean(df$baseline_income_num, na.rm = T)
df$baseline_educ_parents_years_c <- df$baseline_educ_parents_years - mean(df$baseline_educ_parents_years, na.rm = T)
df$baseline_college_year_c <- df$baseline_college_year - mean(df$baseline_college_year, na.rm = T)
df$baseline_gender_numeric_c <- df$baseline_gender_numeric - .5
df$covid_housing_tension_c <- df$covid_housing_tension - mean(df$covid_housing_tension, na.rm = T)
df$covid_phys_dist_c  <- df$covid_phys_dist - mean(df$covid_phys_dist, na.rm = T)

# Add centered variables to the EMA dataset
covid_ema <- merge(covid_ema, df)
```
<br>

Separate the predictor(s) that vary both between- and within-individual in their within and between components.<br>

```{r, message = F, warning = F}
covid_ema <- isolate(d = covid_ema, by = "pID", 
                     value = c("prop_interact_online"), 
                     which = "both")
```
<br>

### Run multilevel regression models
<br>

##### Model 1: Outcome Variable = Negative Affect
<br>

**RQ**: Do students with close friends in college have better quality online interactions (e.g., do they feel less negative affect at the end of the day when a larger proportion of their interactions were online)?<br>

Run regression analysis 1: negative affect ~ close out-degree * prop. of online interactions (within component).<br>

```{r}
options(mc.cores = parallel::detectCores())
f <- stan_glmer(NegativeMood ~ baseline_closest_deg_out_norm_c * prop_interact_online_cw +
                   baseline_income_num_c + baseline_educ_parents_years_c + baseline_college_year_c +
                   baseline_gender_numeric_c + covid_housing_tension_c + covid_phys_dist_c + (1 | groupID:pID),
                data = covid_ema, seed = 123)
save(f, file = sprintf("%s/Models/2.b. Evening-NegAff_Out-Degree_Prop-Online-Interactions.RData", path))
```
<br>
  
##### Model 2: Outcome Variable = Positive Affect
<br>

**RQ**: Do students with close friends in college have better quality online interactions (e.g., do they feel more positive affect at the end of the day when a larger proportion of their interactions were online)?<br>

Run regression analysis 2: positive affect ~ close out-degree * prop. of online interactions (within component).<br>

```{r}
options(mc.cores = parallel::detectCores())
fb <- stan_glmer(PositiveMood ~ baseline_closest_deg_out_norm_c * prop_interact_online_cw +
                   baseline_income_num_c + baseline_educ_parents_years_c + baseline_college_year_c +
                   baseline_gender_numeric_c + covid_housing_tension_c + covid_phys_dist_c + (1 | groupID:pID),
                data = covid_ema, iter = 4000, seed = 123)
save(f, file = sprintf("%s/Models/2.b. Evening-PosAff_Out-Degree_Prop-Online-Interactions.RData", path))
```
<br>

### Summarize results
<br>

Create a table that presents the parameter estimates from the two models together.<br>

```{r, message = F, warning = F}
tab_model(f, fb, show.se = TRUE,
          show.r2 = TRUE, 
          dv.labels = c("Evening Negative Affect",
                        "Evening Positive Affect"),
          pred.labels = c("(Intercept)", 
                          "Close Out-Degree Prior to COVID19",
                          "Online Conversation Proportion (WI)", 
                          "HH Income",
                          "Parents' Education",
                          "Year in College",
                          "Female",
                          "HH Tension",
                          "Physical Distance",
                          "Out-Degree * Online Conversation Prop (WI) Interaction"),
          file = sprintf("%s/Tables/2.b. Evening-NegAff-PosAff-Out-Degree_Prop_Online_Interactions.html", path))
```
<br>

Below, extract the proportion of the posterior distribution that is above or below zero for each predictor of interest separately for the two regression models (evening negative and positive affect).<br>
<br>

##### Model 1: Outcome Variable = Negative Affect 
<br>

Extract the posterior distributions of the parameters from the first regression model.<br>

```{r, message = F, warning = F}
posterior <- as.data.frame(as.matrix(f))
```
<br>

Extract the number of individual points included in a posterior distribution.<br>

```{r, message = F, warning = F}
n <- length(posterior$baseline_closest_deg_out_norm_c)
n
```
<br>

Calculate the proportion of the posterior distribution that is lower than 0 for the main effect of close out-degree on evening negative affect.<br>

```{r, message = F, warning = F}
round(length(which(posterior$baseline_closest_deg_out_norm_c < 0))/n*100,1)
```
<br>

Calculate the proportion of the posterior distribution that is higher than 0 for the main effect of the proportion of online interactions on evening negative affect.<br> 

```{r, message = F, warning = F}
round(length(which(posterior$prop_interact_online_cw > 0))/n*100,1)
```
<br>

Calculate the proportion of the posterior distribution that is lower than 0 for the interaction effect between participants' close out-degree and their proportion of online interactions on evening negative affect.<br> 

```{r, message = F, warning = F}
round(length(which(posterior$`baseline_closest_deg_out_norm_c:prop_interact_online_cw` < 0))/n*100,1)
```
<br>

Calculate the total $R^2$ for the model.<br>

```{r, message = F, warning = F}
round(mean(bayes_R2(f)),2)
```
<br>

##### Model 2: Outcome Variable = Positive Affect 
<br>

Extract the posterior distributions of the parameters from the second regression model.<br>

```{r, message = F, warning = F}
posterior <- as.data.frame(as.matrix(fb))
```
<br>

Extract the number of individual points included in a posterior distribution.<br>

```{r, message = F, warning = F}
n <- length(posterior$baseline_closest_deg_out_norm_c)
n
```
<br>

Calculate the proportion of the posterior distribution that is lower than 0 for the main effect of close out-degree on evening positive affect.<br>

```{r, message = F, warning = F}
round(length(which(posterior$baseline_closest_deg_out_norm_c > 0))/n*100,1)
```
<br>

Calculate the proportion of the posterior distribution that is higher than 0 for the main effect of the proportion of online interactions on evening positive affect.<br> 

```{r, message = F, warning = F}
round(length(which(posterior$prop_interact_online_cw < 0))/n*100,1)
```
<br>

Calculate the proportion of the posterior distribution that is lower than 0 for the interaction effect between participants' close out-degree and their proportion of online interactions on evening positive affect.<br> 

```{r, message = F, warning = F}
round(length(which(posterior$`baseline_closest_deg_out_norm_c:prop_interact_online_cw` > 0))/n*100,1)
```
<br>

Calculate the total $R^2$ for the model.<br>

```{r, message = F, warning = F}
round(mean(bayes_R2(fb)),2)
```
<br>

### General Linear Hypothesis Tests (GLHT)
<br>

##### Model 1: Outcome Variable = Negative Affect 
<br>

Test the hypothesis: does the slope representing the relationship between the proportion of online interactions and evening negative affect differ from zero for 1) students with few friends at school (1.5 SD below mean), 2) students with many friends at school (1.5 SD above mean)?<br>

```{r, message = F, warning = F}
# Calculate mean close out-degree  +/-1.5SD
lw_1.5sd <- round(-1.5*sd(df$baseline_closest_deg_out_norm_c, na.rm = T),3)
lw_1.5sd

up_1.5sd <- round(+1.5*sd(df$baseline_closest_deg_out_norm_c, na.rm = T),3)
up_1.5sd

# Define the number of draws from the posterior distribution
n <- 4000
```
<br>

Test the hypothesis for those with few close friends first.<br>

```{r, message = F, warning = F}
my_hyp_lw <- hypothesis(f, "1*prop_interact_online_cw +
                      -14.884*baseline_closest_deg_out_norm_c:prop_interact_online_cw = 0")
p <- my_hyp_lw$samples
df_hyp <- my_hyp_lw$hypothesis[ ,2:5] %>% 
  mutate(Prop.Above.Zero = length(which(p$H1 > 0))/n) %>% 
  mutate_if(is.numeric, funs(round(., digits = 2))) 
df_hyp
```
<br>

Test the hypothesis for those with many close friends.<br>

```{r, message = F, warning = F}
my_hyp_up <- hypothesis(f, "1*prop_interact_online_cw +
                      14.884*baseline_closest_deg_out_norm_c:prop_interact_online_cw = 0")
p <- my_hyp_up$samples
df_hyp <- my_hyp_up$hypothesis[ ,2:5] %>% 
  mutate(Prop.Above.Zero = length(which(p$H1 > 0))/n) %>% 
  mutate_if(is.numeric, funs(round(., digits = 2))) 
df_hyp
```
<br>

##### Model 2: Outcome Variable = Positive Affect 
<br>

Test the hypothesis: does the slope representing the relationship between the proportion of online interactions and evening positive affect differ from zero for 1) students with few friends at school (1.5 SD below mean), 2) students with many friends at school (1.5 SD above mean)?<br>

Test the hypothesis for those with few close friends first.<br>

```{r, message = F, warning = F}
# Define the number of draws from the posterior distribution
n <- 4000

my_hyp_lw <- hypothesis(fb, "1*prop_interact_online_cw +
                      -14.884*baseline_closest_deg_out_norm_c:prop_interact_online_cw = 0")
p <- my_hyp_lw$samples
df_hyp <- my_hyp_lw$hypothesis[ ,2:5] %>% 
  mutate(Prop.Below.Zero = length(which(p$H1 < 0))/n) %>% 
  mutate_if(is.numeric, funs(round(., digits = 2))) 
df_hyp
```
<br>

Test hypothesis for those with many close friends next.<br>
```{r, message = F, warning = F}
my_hyp_up <- hypothesis(fb, "1*prop_interact_online_cw +
                      14.884*baseline_closest_deg_out_norm_c:prop_interact_online_cw = 0")
p <- my_hyp_up$samples
df_hyp <- my_hyp_up$hypothesis[ ,2:5] %>% 
  mutate(Prop.Below.Zero = length(which(p$H1 < 0))/n) %>% 
  mutate_if(is.numeric, funs(round(., digits = 2))) 
df_hyp
```
<br>