---
title: "Number of In-Person versus Online Interactions in Daily Life During COVID-19 ~ Close Out-Degree"
author: "Ovidia Stanoi"
date: "2025-02-26"
output: html_document
---

### Prepare data for regression analyses. 
<br>

Remove all data from the global environment.<br>

```{r, message = F, warning = F}
remove(list=ls()) 
```
<br>

Load libraries.<br>

```{r, message = F, warning = F}
library("tidyverse")
library("rstanarm")
library("sjPlot")
library("brms")
library("ggpubr")
```
<br>

Specify your directory path below.<br>

```{r, message = F, warning = F}
path <- ""
```
<br>

Open dataset.<br>

```{r, message = F, warning = F}
covid_ema <- read.csv(sprintf("%s/Data/all_data_merged_clean.csv", path)) 
```
<br>

Create a new variable indicating the proportion of interactions reported on a given day that were online.<br>
```{r, message = F, warning = F}
covid_ema$prop_interact_online <- ifelse(!(is.na(covid_ema$NegativeMood)),
                                           covid_ema$SocInt_NUM/(covid_ema$SocInt_NUM + covid_ema$PhysInt_NUM),
                                         NA)
```
<br>                                        

Show the distribution of outcome variables.<br>  
```{r, message = F, warning = F}
ggplot(covid_ema, aes(prop_interact_online)) +
  geom_histogram(fill = "deepskyblue2", color = "deepskyblue4", 
                 alpha = .8, binwidth = .05) + 
  labs(x = "Proportion of Online Interactions",
       y = "Count") +
  geom_vline(xintercept = median(covid_ema$prop_interact_online, na.rm = T), 
             color = "red", linewidth = 1.2) +
  theme_bw() +
  theme(axis.text=element_text(size=16),
        plot.title = element_text(size=18, hjust = .5),
        axis.title=element_text(size=18),
        axis.line = element_line(colour = "gray"),
        panel.border = element_blank()) 
```
        
Extract for each participant their median proportion of online interactions on a typical day during the EMA period, as well as their number of close friend prior to the COVID-19 pandemic, their baseline demographic information, COVID-19 living conditions, number of stressors, and EMA completion rates. All these variables will be added in the regression model.<br>

```{r, message = F, warning = F}
df <- covid_ema %>%
  group_by(pID) %>%
  dplyr::summarise(groupID = unique(groupID), 
                   median_SocInt_NUM = median(SocInt_NUM, na.rm = T),
                   median_PhysInt_NUM = median(PhysInt_NUM, na.rm = T),
                   baseline_closest_deg_out_norm = unique(baseline_closest_deg_out_norm),
                   baseline_income_num = unique(baseline_income_num),
                   baseline_educ_parents_years = unique(baseline_educ_parents_years),
                   baseline_college_year = unique(baseline_college_year),
                   baseline_gender_numeric = unique(baseline_gender_numeric),
                   covid_housing_tension = unique(covid_housing_tension),
                   covid_phys_dist = unique(covid_phys_dist_avg), 
                   EMA_completion_rate = unique(EMA_completion_rate),
                   prop_interact_online = median(prop_interact_online, na.rm = T))
```
<br>

Center continuous predictors around the sample mean and binary variables around zero.<br>

```{r, message = F, warning = F}
df$baseline_closest_deg_out_norm_c <- df$baseline_closest_deg_out_norm - mean(df$baseline_closest_deg_out_norm, na.rm = T)
df$baseline_income_num_c <- df$baseline_income_num - mean(df$baseline_income_num, na.rm = T)
df$baseline_educ_parents_years_c <- df$baseline_educ_parents_years - mean(df$baseline_educ_parents_years, na.rm = T)
df$baseline_college_year_c <- df$baseline_college_year - mean(df$baseline_college_year, na.rm = T)
df$baseline_gender_numeric_c <- df$baseline_gender_numeric - .5
df$covid_housing_tension_c <- df$covid_housing_tension - mean(df$covid_housing_tension, na.rm = T)
df$covid_phys_dist_c  <- df$covid_phys_dist - mean(df$covid_phys_dist, na.rm = T)
df$EMA_completion_rate_c  <- df$EMA_completion_rate - mean(df$EMA_completion_rate, na.rm = T)
```
<br>

### Run regression model
<br>

**RQ**: Do people with more close friends in college have a higher proportion of online interactions on a typical day during the COVID-19 pandemic?<br>

Run regression analysis 1: median proportion of online interactions ~ close out-degree.<br>

```{r}
options(mc.cores = parallel::detectCores())
f <- stan_glmer(prop_interact_online ~ baseline_closest_deg_out_norm_c +
                   baseline_income_num_c + baseline_educ_parents_years_c + baseline_college_year_c +
                   baseline_gender_numeric_c + covid_housing_tension_c + covid_phys_dist_c + 
                   EMA_completion_rate_c + (1 | groupID),
                 data = df, seed = 123)
save(f, file = sprintf("%s/Models/2.a.Prop-Online-Interactions_Out-Degree.RData", path))
```
<br>

### Summarize results
<br>

Create a table that presents the parameter estimates from the two models together.<br>

```{r, message = F, warning = F}
tab_model(f, show.se = TRUE,
          show.r2 = TRUE, 
          dv.labels = c("Median Proportion of Online Interactions"),
          pred.labels = c("(Intercept)", 
                          "Close Out-Degree Prior to COVID19",
                          "HH Income",
                          "Parents' Education",
                          "Year in College",
                          "Female",
                          "HH Tension",
                          "Physical Distance",
                          "EMA Completion Rate"),
          file = sprintf("%s/Tables/2.a.Prop-Online-Interactions_Out-Degree.html", path))
```
<br>